Nodal Discontinuous Galerkin Method for the Euler Equations of Fluid Dynamics

### 2017-07-28 Documents/Euler/dgEulerCurvilinear.tex
updated entropy wave error chart

>>>>

\subsubsection{Entropy Waves (Accuracy Test)}

\begin{table}
  \begin{center}
  \caption{$L^{\infty}$ error and convergence rates for the entropy wave problem.}
  \label{tab:streamingSineWave}
  \begin{tabular}{ccccccccc}
    & \multicolumn{4}{c}{SSP-RK2} & \multicolumn{4}{c}{SSP-RK3} \\
    \cmidrule(r){2-5} \cmidrule(r){6-9}
    $N$ & DG(1) & Rate & DG(2) & Rate & DG(2) & Rate & DG(3) & Rate \\
    \midrule \midrule
    8     & $1.766\times10^{-1}$ & ---  & $2.371\times10^{-3}$ & ---  & $1.700\times10^{-3}$ & ---  & $4.958\times10^{-5}$  & --- \\
    16   & $2.893\times10^{-2}$ &x.xx& $3.236\times10^{-4}$ &x.xx& $1.300\times10^{-4}$ &x.xx& $3.044\times10^{-6}$ &x.xx \\
    32   & $4.203\times10^{-3}$ &x.xx& $6.800\times10^{-5}$ &x.xx& $1.580\times10^{-5}$ &x.xx& $1.983\times10^{-7}$ &x.xx \\
    64   & $6.455\times10^{-4}$ &x.xx& $1.542\times10^{-5}$ &x.xx& $1.971\times10^{-6}$ &x.xx& $1.343\times10^{-8}$ &x.xx \\
    128 & $1.101\times10^{-4}$ &x.xx& $3.659\times10^{-6}$ &x.xx& $2.464\times10^{-7}$ &x.xx& $9.737\times10^{-10}$ &x.xx \\
    256 & $2.109\times10^{-5}$ &x.xx& $8.904\times10^{-7}$ &x.xx& $3.081\times10^{-8}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx \\
    \midrule \midrule
  \end{tabular}
  \end{center}
\end{table}

\subsubsection{Sound Waves}
